PANCHANGE_data_preprocessing

### 2020-08-25 PANCHANGE_analysis.Rmd
add autism chunk for harmonising
harmonising age categories with RAMP

# Exclusion
Filter data frame to exclude participants that never answered COPING
```{r exclusion criteria dat}
dat <- dat.raw %>%
  filter(
    (data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")
  )
```

@@

@@

+++CHECK OVERLAP BETWEEN TESTS and probable COVID

>>>>

# Exclusion

## COPING
Filter data frame to exclude participants that never answered COPING
```{r exclusion criteria dat}
dat <- dat.raw %>%
  filter(
    (data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")
  )
```

@@

```{r}
dat.raw %>%
  freq(age_category_full)
```

## GAD
```{r}
dat.gad <- dat.raw %>%
  drop_na()
  filter(
    (data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data")
  )

dim(dat.gad)
```

@@

### 2020-08-25 PANCHANGE_data_preprocessing2020-07-15.Rmd
harmonising age categories with RAMP

dem.raw.id <- dem.raw.id %>%
    mutate(
      age_category_full =
        recode_factor(
          age_category_numeric, 
          "1" = "16 to 18 years",
          "2" = "19 to 25 years",
          "3" = "26 to 35 years",
          "4" = "36 to 45 years",
          "5" = "46 to 55 years",
          "6" = "56 to 65 years",
          "7" = "66 to 70 years",
          "8" = "71 to 75 years",
          "9" = "76 to 80 years",
          "10" = "81 to 85 years",
          "11" = "86 to 90 years",
          "12" = "91 to 100 years",
          "13" = "Above 100 years"
          )
    )

>>>>

dem.raw.id <- dem.raw.id %>%
    mutate(
      age_category_full =
        recode_factor(
          age_category_numeric, 
          "1" = "16-18",
          "2" = "19-25",
          "3" = "26-35",
          "4" = "36-45",
          "5" = "46-55",
          "6" = "56-65",
          "7" = "66-70",
          "8" = "71-75",
          "9" = "76-80",
          "10" = "81-85",
          "11" = "86-90",
          "12" = "91-100",
          "13" = "100+"
          )
    )
